Fig3

### 2020-05-12 analysis/figure-3.Rmd
attempting to save and read DEGs and vsd files

```{r PCA}
# pca
pca1f <- subsetmakepca("pituitary", charlevels, "female")	
pca2f <- makefvizdf("pituitary", charlevels, "female")

@@

pca1 <- subsetmakepca("pituitary", charlevels, sexlevels)	
pca2 <- makefvizdf("pituitary", charlevels, sexlevels)

@@

```{r}
# `candidatevsd` loaded with `source("../R/wrangledata.R")`

@@

hypothesisDEGs <- c(hypothesisDEGs, WGCNAgenes) %>% unique()

>>>>

```{r PCA}
# pca relies on count data from limma

pca1f <- subsetmakepca("pituitary", charlevels, "female")	
pca2f <- makefvizdf("pituitary", charlevels, "female")

@@

pca1 <- subsetmakepca("pituitary", charlevels, sexlevels)	
pca2 <- makefvizdf("pituitary", charlevels, sexlevels)	
```

@@

```{r}
candidatevsd <- read_csv("../results/03_candidatevsd.csv")
head(candidatevsd)

@@

hypothesisDEGs <- read_csv("../results/03_hypothesisDEGs.csv")
hypothesisDEGs <- c(hypothesisDEGs, WGCNAgenes) %>% unique()
